\section{Introduction }
The increase in greenhouse gas emissions, contributed by a high volume of traffic along with traffic jams, continues to increase every year except for these recent years due to the COVID-19 pandemic. However, in cities such as New York, a driver would still spend around 100 hours extra due to congestion\cite{TrafficReport}, thus increasing emissions of greenhouse gasses and increasing the cost of transportation for the driver.

There are several proposed approaches to help reduce traffic in cities with recurring traffic jams, and one of these approaches is to use vehicle to vehicle (V2V) communication along with autonomous vehicles. These are two technologies that are in constant development and the complexity of these systems increase year after year.

These technologies allow cities to more efficiently use the current infrastructure instead of expanding on their current road network.

This report aims to answer whether or not autonomous vehicles using vehicle to vehicle communication can reduce traffic in cities with recurring traffic jams. This is done by creating a model of a simple highway system with several vehicles in it, and simulating a base case of regular vehicles against different proportions of vehicles implementing these technologies.

The report will be structured in sections and each section can be described as follows: 
% put this in itemize
\begin{itemize}
    \item Section 2 will introduce some of the concepts and the problem statement for this report.
    \item Section 3 will discuss the proposed model that was used to create the simulations
    \item Section 4 will discuss how this model was implemented along with the visualization of the simulations.
    \item Section 5 will analyze the simulations that were conducted and discuss the different experiments.
    \item Section 6 and 7 will conclude the report, with a discussion about the results and future work to be done to the model and simulator along with a short conclusion to the report.
\end{itemize}